%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Oliver Earl}}}} % First name
	
	\vspace{6pt}
	
	{\Large Software Engineer $\sim$ Mental Health Volunteer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\icon{Globe}{11}{\href{https://www.oliverearl.co.uk}{oliverearl.co.uk}}\\ 
    \icon{Phone}{11}{\href{tel:07821600793}{07821600793}}\\
    \icon{MapMarker}{11}{Birmingham, UK}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:oliver@oliverearl.co.uk}{oliver@oliverearl.co.uk}}\\	
    \icon{Github}{11}{\href{https://github.com/oliverearl}{github.com/oliverearl}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/oliverearl}{/in/oliverearl}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    %Dummy text
I'm a full-stack web developer with multiple years of experience repeatedly delivering clean, performant, and test-backed code for a wide range of use cases, built upon a concrete theoretical foundation from teaching and studying computer science. Competent in spoken and written German.
 
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Backend:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Laravel 5.6-10.x, Lumen, CodeIgniter 3.x, WordPress, PHP, Node.js, MySQL, PostgreSQL, MongoDB, Redis, Websockets, REST, GraphQL, Docker, GitHub CI/CD, Bash, PHPUnit, Pest
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Frontend:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
    Vue.js 2.x/3.x, JavaScript, TypeScript, Nuxt.js, Livewire, Inertia.js, jQuery, Sass, Tailwind, Bootstrap, Jest, Laravel Dusk
    \end{minipage}
    
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Relevant Experience}
\begin{entrylist}
	\entry
        {Jan/21 -- Present}
		{Software Developer}
		{Stickee Technology}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item \textbf{Core developer on \textit{Project Stardust}.} A high-performance e-commerce and mobile network platform built using Laravel, TypeScript, Inertia.js, and Tailwind. Releasing in Q1 2024.
            \item \textbf{Recently led the development of an e-commerce platform for a major UK phone network.} Including the later integration of \textit{Buy Now Pay Later} using PayPal Credit; leading to dramatically increased network uptake and sales revenue. 
            \item \textbf{Lead developer on a content distribution and management platform for a leading international client. } Notable for refactoring the systems that ingest large amounts of assets and semi-structured data from the client, which are then processed, optimised and distributed to resellers using the cloud.
            \item \textbf{Heavily involved in the company's open source efforts. }Predominantly \textit{Canary}, a code styling and refactoring tool written using Laravel Zero, as well as libraries used for reactive data logging and alerting.
        \end{itemize} 
        }
	\entry
		{Mar/22 -- Present}
		{Volunteer Software Developer}
		{Nightline Association}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item \textbf{Significant contributor to \textit{Portal}.} A centralised software suite that facilitates the work of student-run listening services across the UK. Much of this work is in the IM module, which handles thousands of anonymous messages and call logs every night.
            \item \textbf{Currently leading the development of an accreditation management module.} The module will migrate the existing laborious spreadsheet based system to an asynchronous, record-keeping workflow.
            \item \textbf{Recently finished the Find My Nightline functionality}. Comprised of making local branch data available via REST API in Portal, and producing a WordPress plugin that uses Vue.js to present that data. Currently used up to hundreds of times a day on the charity's homepage.
            \item \textbf{Involved in community and team-building efforts.} This includes the onboarding of new volunteers, code reviewing, and pair programming and knowledge sharing with those less experienced.
        \end{itemize} 
        }
	\entry
		{Jan/20 -- Dec/20}
		{Trainee Teacher of Computer Science}
		{Arden Academy}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Taught GCSE and A Level Computer Science at one of the top public secondary schools in the UK.
        \end{itemize} 
        }

% 	\entry
% 		{Sep/15 -- Sep/19}
% 		{Demonstrator}
% 		{Aberystwyth University}
% 		{\vspace{-10pt}
%         \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
%             \item Part-time teaching assistant on modules including Linux, Arduino C++, and JavaScript.
%         \end{itemize} 
%         }

% 	\entry
% 		{Jun/16 -- Dec/16}
% 		{Frontend Developer Intern}
% 		{Amadeus IT Group}
% 		{\vspace{-10pt}
%         \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
%             \item Prototyping Angular 1.x/2.x frontends for backend web applications. Working language of German.
%         \end{itemize} 
%         }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
	\entry
        {Sep/19 -- Dec/20}
		{PGCE Post-Compulsory Education and Training}
		{Birmingham City University}
		{\textit{Completion took additional time due to COVID-19 pandemic.}}
	\entry
        {Sep/18 -- Sep/19}
		{MSc Software Engineering}
		{Aberystwyth University}
		{Merit}
  	\entry
        {Sep/14 -- Jul/18}
		{BSc(Hons) Computer Science with German}
		{Aberystwyth University}
		{1st class}
\end{entrylist}
% \pagebreak

%----------------------------------------------------------------------------------------
%	MISC EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Miscellaneous Experience}
\begin{entrylist}
	\entry
        {Jun/21 -- Jun/23}
		{Regional Coordinator}
		{Nightline Association}
		{The elected representative responsible for overseeing Nightline listening services within Wales, ensuring that they operate within the guidelines set by the central organisation and are adequately supported with their day-to-day operations.}
	\entry
		{Feb/15 -- Sep/19}
		{Listening Volunteer}
		{Aberystwyth Nightline}
		{Volunteer with more than 600 hours of helpline support, 550 in peer-to-peer support, and 230 in Active Listening training. Holds a L2 in Counselling Skills and is certified in both workplace mental health first aid and in applied suicide intervention. (ASIST)}
\end{entrylist}
\end{document}
